### 2020-05-21 paper.tex
Fix Copy-Paste

In order to prepare to give an answer on the first research question, we started with a series of informal interviews. We talked to professionals about their experiestack defined through our research area since we were interested in as many different perspective on the topic as possible in this early stage. Eventually, we interviewed five engince in working with RP in their daily jobs. We did not limit the selection of our interview partners by the tech neers: Four work or worked more recently with Angular\footnote{\url{https://angular.io/}} and ngrx\footnote{\url{https://ngrx.io/}} to develop frontend applications. Two of them stated to have more explicit experience with RxJS further. The fifth subject works currently with a combination of akka\footnote{\url{https://akka.io/}} and akka-streams in Scala to create backend applications. The agenda available in Appendix~\ref{sec:interviewquestions} was used to maintain focus during the interview sessions.

@@

We could verify previously gathered interview data with the results from the new reports: The subjects tend to manually add log statements to their code in order to understand its behavior, especially when things get more complex. Three subjects even claimed using specialized logging functionalities provided by rxjs-spy\cite{rxjsspy}. As the subjects stated, the knowledge about additional events made visible helped in situations where they needed to find problems within a graph composing multiple asynchronous data sources on multiple levels. Without it, they would have been blind to what actually happend within the system.

>>>>

In order to prepare to give an answer on the first research question, we started with a series of informal interviews. We talked to professionals about their experience in working with RP in their daily jobs. We did not limit the selection of our interview partners by the tech stack of including RxJS since we were interested in as many different perspectives on the topic as possible in this early stage. Eventually, we interviewed six engineers: Four work or worked more recently with Angular\footnote{\url{https://angular.io/}} and ngrx\footnote{\url{https://ngrx.io/}} to develop frontend applications. Two of them stated to have more explicit experience with RxJS further. One subject works currently with a combination of akka\footnote{\url{https://akka.io/}} and akka-streams in Scala to create backend applications. The sixth subject was the creator of rxfiddle. The agenda available in Appendix~\ref{sec:interviewquestions} was used to maintain focus during the interview sessions.

@@

We could verify previously gathered interview data with the results from the new reports: The subjects tend to manually add log statements to their code in order to understand its behavior, especially when things get more complex. Three subjects even claimed using specialized logging functionalities provided by rxjs-spy\cite{rxjsspy}. As the subjects stated, the knowledge about additional events made visible helped in situations where they needed to find problems within a graph composing multiple asynchronous data sources on multiple levels. Without it, they would have been blind to what actually happened within the system.
